Comparing Cross Validation Methods for Penalized Cox Regression

### 2018-02-13 cross-validation.tex
reorganize simulation section

\section{Simulation Studies}
%reformulate this section with%
%3.1 comparison between the three methods
%3.2 discussion about stability issue for ungrouped methods
%3.3 comparison with AIC
%3.4 explaining why deviance residuals do not work well

  \subsection{Simulation Settings}

@@

  \subsection{Simulation Results}

    \subsubsection {Stability}
   While the ungrouped cross-validated likelihood is an intuitive way to carry out cross-validation, it is quite unstable when it runs into cases where the number of observed events in some fold is really small. As is illustrated in Figure 5, cases of undefined cross-validation error would increase when censoring increases or when number of folds increases.

    \subsubsection {Simulations in Low Dimensional Settings}

   The simulation experiments were first conducted under lower dimension settings. Number of observations n is set to be 100. Dimension of the data p is set to be 100. 200 replications were used. Censoring percentage, number of folds used in cross-validation, number of non-zero $\beta$s and the magnitude of the $\beta$000000000s were varied in several different simulation scenarios. Patterns and results shown in various simulation scenarios are consistent with one another. Figure 5 and Figure 6 illustrates one simulation scenario, where about 10$\%$ of which were set to be censored and 10 of the $\beta$s were set to be non-zero and 10 folds were used for cross validation. The x - axis of the plots are the magnitude of the non-zero $\beta$ coefficients.

@@

    \subsubsection {Simulations in High Dimensional Setting}

@@

  \vspace{20 mm}
    \subsubsection {Comparisons with Information Criteria}
    \par We also compared cross-validation with information criteria AIC and BIC. Simulation studies were conducted in lower dimension and higher dimension respectively. As is illustrated in Figure 7, in lower dimension, AIC tends to perform more liberal and BIC tends to perform more conservative than the optimal $\lambda$. While the cross-validation methods are also conservative, most of them are less conservative than BIC. In terms of MSE, cross-validation methods yield smaller MSE than the information criteria. In higher dimension, both BIC and AIC tend to be more liberal than the optimal $\lambda$ and yield larger MSE.

@@

>>>>

\section{Simulation Studies}

@@

    \subsection {Simulations Comparing Cross-validation Approaches}
  %need to change figures to include the new cross-validated deviance residuals
   The simulation experiments were first conducted under lower dimension settings. Number of observations n is set to be 100. Dimension of the data p is set to be 100. 200 replications were used. Censoring percentage, number of folds used in cross-validation, number of non-zero $\beta$s and the magnitude of the $\beta$s were varied in several different simulation scenarios. Patterns and results shown in various simulation scenarios are consistent with one another. Figure 5 and Figure 6 illustrates one simulation scenario, where about 10$\%$ of which were set to be censored and 10 of the $\beta$s were set to be non-zero and 10 folds were used for cross validation. The x - axis of the plots are the magnitude of the non-zero $\beta$ coefficients.

@@

@@

 \subsection {Stability}
   While the ungrouped cross-validated likelihood is an intuitive way to carry out cross-validation, it is quite unstable when it runs into cases where the number of observed events in some fold is really small. As is illustrated in Figure 5, cases of undefined cross-validation error would increase when censoring increases or when number of folds increases.

    \subsection {Comparisons with Information Criteria}
	%need to change the figures to have fewer lines
    \par We also compared cross-validation with information criteria AIC and BIC. Simulation studies were conducted in lower dimension and higher dimension respectively. As is illustrated in Figure 7, in lower dimension, AIC tends to perform more liberal and BIC tends to perform more conservative than the optimal $\lambda$. While the cross-validation methods are also conservative, most of them are less conservative than BIC. In terms of MSE, cross-validation methods yield smaller MSE than the information criteria. In higher dimension, both BIC and AIC tend to be more liberal than the optimal $\lambda$ and yield larger MSE.

@@

 \subsection {Issues with Deviance Residual}
